InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-23 paper.tex
Apply suggestions from Levi
Co-authored-by: LeviUniAcc <102458061+LeviUniAcc@users.noreply.github.com>

Another tool to automatically detect generated text is \textbf{GLTR}. It applies different baseline statistical methods to detect generation artefacts. To do so, it needs access to a certain model, for which it can predict, whether the text is likely to be generated. The text is compared with the distribution of possible consecutive words given the semantic context. The tool calculates which word would have been predicted as next word at each token in the text and allows to colour which words are how likely to appear by the model at a given position and context. If a text is coloured completely green, a lot of words have a high chance, that they would have been predicted at this position by e.g. the currently hosted GPT2 117M model. Therefore, it is likely that a mostly green coloured text is generated by the GPT2 model. This approach can also be used for other models. \cite{gehrmann2019gltr}

A more recent approach is presented in \cite{zellers2020defending}. With the aim to investigate in the detection of AI generated fake news, the authors created a model called \textbf{Grover}, which is on the one hand able to generate fake news, but on the other hand also pretty reliably detects, whether a given text is AI-generated by itself. The study also elaborates on how to deal with the issue on generated fake news. Therefore, inspired by IT security research, they advocate for the release of such models to allow the development of effective countermeasures like detector models.

@@

We used the aforementioned models for generating and detecting texts and images. As for image processors, one was already given in the description of the "InformatiCup2024" \cite{InformatiCup}, the image noising using the Gaussian noise. Image noise is the random variation of brightness or color information in images produced by the sensor and circuitry of a scanner or digital camera. The reason why the Gaussian one, also called normal noise, is being used, is because it is being caused by natural sources and the most common noise that affects images naturally \cite{mohammed2016study}. \\
There are several types of noise that can affect images. Some of these noise models are: Gaussian noise, White noise, Fractal noise, Salt \& Pepper noise, Periodic noise, Quantization noise, Speckle noise, Poisson noise, Poisson-Gaussian noise, Structured noise, Gamma noise and Rayleigh noise \cite{gonzalez2009digital}. The three common types of image noise are: Gaussian noise, Salt \& Pepper noise, and Speckle noise \cite{al2010comparative}. That is why we used those three, as well as the Poisson noise.

>>>>

@@

We used the aforementioned models for generating and detecting texts and images. As for image processors, one was already given in the description of the "InformatiCup2024" \cite{InformatiCup}, the image noising using the Gaussian noise. Image noise is the random variation of brightness or color information in images produced by the sensor and circuitry of a scanner or digital camera. We used gaussian noice, because it can occure due to natural sources and it is the most common noise that affects images naturally. \cite{mohammed2016study}

There are several types of noise that can affect images. Some of these noise models are: Gaussian noise, White noise, Fractal noise, Salt \& Pepper noise, Periodic noise, Quantization noise, Speckle noise, Poisson noise, Poisson-Gaussian noise, Structured noise, Gamma noise and Rayleigh noise \cite{gonzalez2009digital}. The three common types of image noise are: Gaussian noise, Salt \& Pepper noise, and Speckle noise \cite{al2010comparative}. That is why we used those three, as well as the Poisson noise.

As for text processors, we evaluated three different methods of augmenting generated texts. The first approach was to replace every white-space in a given text by two white-spaces. The second approach was to add some typos to the texts. This has been implemented based on the nlpaug library, which is capable of simulating certain typos as if they were made on a keyboard by a human. The typos include mistakes, like hitting a wrong key, which is close to the right one. This results in typos often created by humans. The last approach is a translator, which has been used to translate the given text into a certain language (in this case French) and re-translate it into english. As translators are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.
